---
title: "Analysis of the Corpus of Oz Early English - Part 1: Data Preparation"
author: "Anonymous"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  bookdown::html_document2: default
bibliography: Bibliography.bib
link-citations: yes
---

# Introduction

This document shows an analysis of Corpus of Oz Early English  (COOEE) [@fritz2004cooee]. 

## Aims

* Find keywords  (part 2)

* Check for distribution of keywords by date (mosaic plot)  (part 2)

* Create network of keywords (network analysis)  (part 2)

* Find topics (topic modeling) (part 3)

* Error analysis (misspelled words, words not in dictionary) (part 4)

# Data Processing

In a first step, the session is prepared by installing packages.


```{r cooee_01_01, eval = F, message=FALSE, warning=FALSE}
# load packages
install.packages("tidyverse")
install.packages("tidytext")
install.packages("tidyr")
install.packages("tm")
install.packages("tokenizers")
install.packages("qdap")
install.packages("textstem")
install.packages("corpus")
install.packages("ngram")
```

Now, we activate the packages, set options, load relevant functions, and defining the path to the data.

```{r cooee_01_03}
# set options
options(stringsAsFactors = F)
options(scipen = 999)
# load packages
library(tidyverse)
library(tidytext)
library(tidyr)
library(tm)
library(tokenizers)
library(qdap)
library(textstem)
library(corpus)
library(ngram)
library(quanteda)
# specify path to corpus
corpuspath <- "D:\\Uni\\Korpora\\Original\\COOEE\\COOEE-single_files"
# specify path to metadata
metapath <- "D:\\Uni\\Korpora\\Original\\COOEE/COOEE.XLS"
# for pos-tagging objects in R
source("D:\\R/POStagObject.R") 
```


In a next step, we load and process the corpus data.


```{r  cooee_01_05, warning=F, message=F}
# load corpus files
cooeefiles = list.files(path = corpuspath, all.files = T, full.names = T, recursive = T, ignore.case = T, include.dirs = T)
# load and unlist corpus
cooee <- sapply(cooeefiles, function(x) {
  x <- scan(x, what = "char", sep = "", quote = "\"", quiet = T, skipNul = T)
  x <- stringr::str_squish(x)
  x <- paste0(x, collapse = " ")
  x <- unlist(x)
} )
# inspect data
str(cooee)
```

Convert data into a data frame.

```{r  cooee_01_07, warning=F, message=F}
cooeedf <- data.frame(cooeefiles, cooee) %>%
  dplyr::rename(Nr = colnames(.)[1],
                Rawtext = colnames(.)[2]) %>%
  dplyr::mutate(Nr = stringr::str_replace_all(Nr, ".*/(.*).txt", "\\1")) %>%
  as.tibble()
# inspect
head(cooeedf)
```


Extract metadata (corpus, file, date, etc.)

```{r  cooee_01_09, warning=F, message=F}
meta <- readxl::read_xls(metapath)
cnames <- as.vector(unlist(meta[1,])) %>%
  stringr::str_remove_all(" ")
cnames[c(14:16)] <- c("Words", "GenderAddressee", "StatusAddressee")
meta <- meta[2:nrow(meta),]
colnames(meta) <- cnames
meta <- meta  %>%
  dplyr::mutate(id = 1:nrow(.))
# inspect
head(meta)
```

Combine 

```{r  cooee_01_11, warning=F, message=F}
# combine into table
cooeed <- meta %>% dplyr::inner_join(cooeedf, by = "Nr")
# inpspect
head(cooeed)
```

Process and clean data

```{r cooee_01_13, warning=F, message=F}
# clean files
cooeed_clean <- cooeed %>%
  dplyr::mutate(Text = Rawtext) %>%
  dplyr::mutate(Text = stringr::str_remove_all(Text, "\\[/{0,1}.*?\\]"),
                Text = stringr::str_remove_all(Text, "\\</{0,1}.*?\\>"),
                Text = stringr::str_remove_all(Text, "\\{|\\}"),
                Datecat = dplyr::case_when(as.numeric(YearWriting) < 1800 ~ "1788-1800",
                                           as.numeric(YearWriting) < 1820 ~ "1801-1820",
                                           as.numeric(YearWriting) < 1840 ~ "1821-1840",
                                           as.numeric(YearWriting) < 1860 ~ "1841-1860",  
                                           as.numeric(YearWriting) < 1880 ~ "1861-1880", 
                                           as.numeric(YearWriting) <= 1900 ~ "1881-1900",
                                           TRUE ~ YearWriting),
                Datecat = factor(Datecat)) %>%
  # Words
  dplyr::mutate(Words = stringr::str_replace_all(Text, "\\W", " "),
                Words = stringr::str_squish(Words),
                Words = stringr::str_count(Words, "\\w+"))
# inspect
head(cooeed_clean)
```






```{r cooee_01_17}
# define stopword regex
stopwords_regex = paste(tm::stopwords('en'), collapse = '\\b|\\b')
stopwords_regex = paste0('\\b', stopwords_regex, '\\b')
# remove stopwords
cooeed_clean <- cooeed_clean %>%
  dplyr::filter(Register == "PrW") %>%
  dplyr::mutate(Text_clean = stringr::str_remove_all(tolower(Text), stopwords_regex),
                Text_clean = stringr::str_remove_all(Text_clean, "[^[:alpha:] ]"),
                Text_clean = stringr::str_squish(Text_clean))
# save data
base::saveRDS(cooeed_clean, file = here::here("data", "cooeed_clean.rda"))
# inspect
head(cooeed_clean)
```



Check data

```{r cooee_01_19}
table(cooeed_clean$Datecat)
```

# Control corpus

We now generate a parallel table of data from letters not written by Irish emigrants

```{r  cooee_01_23, warning=F, message=F}
controlpath <- "D:\\Uni\\Korpora\\Original\\A Corpus of late 18c Prose\\2468/orford.txt"
# load and unlist corpus
control <- scan(controlpath, what = "char", sep = "", quote = "\"", quiet = T, skipNul = T) %>%
  stringr::str_squish() %>%
  paste0(collapse = " ") %>%
  stringr::str_split("<A ") %>%
  unlist()
control <- control %>%
  as.data.frame() %>%
  dplyr::rename(Rawtext = colnames(.)[1])
# inspect
str(control)
```



```{r  cooee_01_25, warning=F, message=F}
# clean files
control_clean <- control %>%
  dplyr::filter(Rawtext != "") %>%
  dplyr::mutate(Text = Rawtext) %>%
  dplyr::mutate(Text = stringr::str_remove_all(Text, "\\[/{0,1}.*?\\]"),
                Text = stringr::str_remove_all(Text, "\\</{0,1}.*?\\>"),
                Text = stringr::str_remove_all(Text, "\\{|\\}"),
                Text_clean = stringr::str_remove_all(Text, "[^[:alpha:] ]"),
                Text_clean = stringr::str_replace_all(tolower(Text_clean), stopwords_regex, ""),
                id = 1:nrow(.)) %>%
  dplyr::mutate(YearWriting = gsub(".*<O \\?{0,2}([0-9]{2,4})\\?{0,2}.{0,2}>.*", "\\1", Rawtext),
                YearWriting = stringr::str_pad(YearWriting, 4, side = "right", pad = "0"),
               Datecat = dplyr::case_when(as.numeric(YearWriting) < 1800 ~ "1788-1800",
                                           as.numeric(YearWriting) < 1820 ~ "1801-1820",
                                           as.numeric(YearWriting) < 1840 ~ "1821-1840",
                                           as.numeric(YearWriting) < 1860 ~ "1841-1860",  
                                           as.numeric(YearWriting) < 1880 ~ "1861-1880", 
                                           as.numeric(YearWriting) <= 1900 ~ "1881-1900",
                                           TRUE ~ "unknown"),
                Datecat = factor(Datecat))
# save data
base::saveRDS(control_clean, file = here::here("data", "control_clean.rda"))
# inspect data
head(control_clean)
```

# Corpus Exploration

## COOEE

```{r train, message=F, warning=F}
cooeetb <- cooeed_clean %>%
  dplyr::select(Birth, Gender, Origin, Age, Status, Arrival, Abode, YearWriting, 
                PlaceWriting, TextT, Words, Text_clean, Datecat) %>%
  dplyr::mutate(Gender = dplyr::case_when(Gender == "m" ~ "male", 
                                          Gender == "f" ~ "female",
                                          TRUE ~ "unknown")) %>% 
  dplyr::rowwise() %>%
  dplyr::mutate(Tokens = length(unlist(tokenize_fasterword(Text_clean))),
                Types = length(table(unlist(tokenize_fasterword(Text_clean)))))
# inspect
head(cooeetb)
```

tab: date, gender, types, tokens



```{r}
tab01 <- cooeetb %>%
  dplyr::group_by(Datecat, Gender) %>%
  dplyr::summarise(Letters = n(),
                   Types = sum(Types),
                   Tokens = sum(Tokens),
                   MeanLength = round(Tokens/Letters, 1))
readr::write_delim(tab01, here::here("tables", "tab01.txt"), delim = "\t")
# inspect
tab01
```



```{r}
tab02 <- cooeetb %>%
  dplyr::group_by(Gender) %>%
  dplyr::summarise(Letters = n(),
                   Types = sum(Types),
                   Tokens = sum(Tokens))
readr::write_delim(tab02, here::here("tables", "tab02.txt"), delim = "\t")
# inspect
tab02
```

check percentage of letters written by women


```{r}
# percent women
27/(378+27)*100
# average length
797569/405


```

## CLMP

inspect control data

```{r}
head(control_clean)
```

generate overview table for control corpus by year

```{r train, message=F, warning=F}
controltb <- control_clean %>%
  dplyr::select(YearWriting, Text, Datecat) %>%
  dplyr::mutate(Text = stringr::str_squish(Text)) %>%
  dplyr::rowwise() %>%
  dplyr::mutate(Tokens = length(unlist(tokenize_fasterword(Text))),
                Types = length(table(unlist(tokenize_fasterword(Text)))))
# inspect
head(controltb)
```

generate overview table for control corpus by period

```{r}
tab03 <- controltb %>%
  dplyr::group_by(Datecat) %>%
  dplyr::summarise(Letters = n(),
                   Types = sum(Types),
                   Tokens = sum(Tokens),
                   MeanLength = round(Tokens/Letters, 1))
readr::write_delim(tab03, here::here("tables", "tab03.txt"), delim = "\t")
# inspect
tab03
```

# Map

check number of letters by region

```{r}
table(cooeed_clean$PlaceWriting)
```

load packages and and data

```{r}
# load packages
library(tmap) 
library(here)
library(rgdal)
# load shape files
ozmap <- readOGR(dsn = here::here("data/shapes", "AshmoreAndCartierIslands.shp"), stringsAsFactors = F)
```

process data

```{r}
# convert the data into tidy format
ozmapt <- broom::tidy(ozmap, region = "name")
# inspect data
head(ozmapt)
```

clean map data

```{r}
# extract names of states and their long and lat
cnames <- ozmapt %>%
  dplyr::group_by(id) %>%
  dplyr::summarise(long = mean(long),
                   lat = mean(lat)) %>%
  dplyr::filter(id != "Ashmore and Cartier Islands",
                id != "Christmas Island",
                id != "Cocos (Keeling) Islands",
                id != "Coral Sea Islands Territory",
                id != "Heard Island and McDonald Islands",
                id != "Jervis Bay Territory",
                id != "Norfolk Island",
                id != "Australian Capital Territory") %>%
  dplyr::mutate(long = ifelse(id == "Queensland", long-5, long ),      # to left
                long = ifelse(id == "New South Wales", long-2, long ),
                long = ifelse(id == "Northern Territory", long-1, long ),
                lat = ifelse(id == "New South Wales", lat+2, lat ),    # up
                lat = ifelse(id == "Northern Territory", lat-5, lat ),
                lat = ifelse(id == "Victoria", lat+1, lat ),
                lat = ifelse(id == "South Australia", lat+5, lat ),
                lat = ifelse(id == "Western Australia", lat-3, lat )) %>%
  dplyr::mutate(id = ifelse(id == "New South Wales", "New South Wales\n(196 letters)", id ),
                id = ifelse(id == "Queensland", "Queensland\n(16 letters)", id ),
                id = ifelse(id == "South Australia", "South Australia\n(31 letters)", id ),
                id = ifelse(id == "Tasmania", "Tasmania\n(28 letters)", id ),
                id = ifelse(id == "Victoria", "Victoria\n(240 letters)", id ),
                id = ifelse(id == "Western Australia", "Western Australia\n(87 letters)", id ))
# inspect
cnames
```

define colors for states and text

```{r}
# define colors
#library(scales)
#clrs <- viridis_pal()(15)
# inspect
clrs <- c("gray99",
          "gray99",
          "gray99",
          "gray99",
          "gray99",
          "gray99",
          "gray99",
          "gray40", # NSW
          "gray99",
          "gray95", # NT
          "gray90", # QLD
          "gray80", # SA
          "gray85", # TAS
          "gray25", # VIC
          "gray70") # wa
tclrs <- c("white", # NSW
          "gray20", # NT
          "gray20", # QLD
          "gray20", # SA
          "gray20", # TAS
          "white", # VIC
          "gray20") # wa
```


generate map

```{r}
# plot ozmap
p <- ggplot() +
  # plot map
  geom_polygon(data = ozmapt, 
               aes(x = long, y = lat, group = group, fill = id), 
               asp = 1, colour = NA) +
  # add text
  geom_text(data = cnames, aes(x = long, y = lat, label = id), 
            size = 2.5, color = tclrs, fontface = "bold", 
            check_overlap = T) +
  # color states
  scale_fill_manual(values = clrs) +
  # define theme and axes
  theme_void() +
  scale_x_continuous(name = "Longitude", limits = c(113, 155)) +
  scale_y_continuous(name = "Latitude", limits = c(-45, -10)) +
  # def. background color
  theme(panel.background = element_rect(fill = "white",
                                        colour = "white",
                                        size = 0.5, linetype = "solid"),
        legend.position = "none")
ggsave(file = here::here("images", "letter_map.png"), 
         height = 4,  width = 5, dpi = 320)
# show plot
p
```


# Outro

```{r  cooee_01_29}
sessionInfo()
```


# References